Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-06 ms.tex
avoid referring to SFD i100 as IRAS whenever possible

\begin{deluxetable}{rrrrrr} 
\tabletypesize{\scriptsize}
\tablecolumns{6} 
\tablewidth{0pc} 
\tablecaption{\label{tab:global} Global Model Parameters} 
\tablehead{
\colhead{Model} &
\colhead{Data} &
\colhead{$f_1$} &
\colhead{$q_1/q_2$} & 
\colhead{$\beta_1$} & 
\colhead{$\beta_2$}
}
\startdata
 1 & FIRAS+\IRAS & 0.0363 & 13.0 & 1.67 & 2.70 \\
 2 & \PLANCK+\IRAS & 0.0267 & 3.68 & 1.19 & 2.61 \\ [-2ex]
\enddata
\end{deluxetable}

@@

The MCMC fitting procedure described in $\S$\ref{sec:fitting} is performed
separately for both model 1 (FIRAS+\IRAS) and model 2 (\PLANCK+\IRAS), each
defined by their respective global parameters listed in Table \ref{tab:global}.

@@

The \PLANCK~100-353 GHz data are provided in units of thermodynamic 
$\delta T$, while \verb|i100| and the higher frequency HFI maps are provided in
units of MJy/sr. Although the aforementioned preprocessing steps were conducted
with each map in its native units, we converted the 217 GHz and 353 GHz 
measurements to MJy/sr according to \cite{planckresponse} prior to performing 
SED fits.

%i think it's table 6 that I specifically want to cite within the ``spectral
%response'' paper, but i need to check that those values are consistent
% with the ones i actually used from the other document ``HFI-unit conversion 
%and colour correction instructions v1.2''

\subsection{Fitting Parameters}
In order to fit the \PLANCK/\IRAS~dust SED, we must combine the underlying 
two-component spectrum $M_{\nu}$ with the bandpass corrections $b_{\nu_i}$ to 
yield predictions which can be compared against the observed broadband 
intensities. The model-predicted broadband intensities $\tilde{I}_{\nu_i}$ are 
given by:

>>>>

\begin{deluxetable}{rrrrrr} 
\tabletypesize{\scriptsize}
\tablecolumns{6} 
\tablewidth{0pc} 
\tablecaption{\label{tab:global} Global Model Parameters} 
\tablehead{
\colhead{Model} &
\colhead{Data} &
\colhead{$f_1$} &
\colhead{$q_1/q_2$} & 
\colhead{$\beta_1$} & 
\colhead{$\beta_2$}
}
\startdata
 1 & FIRAS+\verb|i100| & 0.0363 & 13.0 & 1.67 & 2.70 \\
 2 & \PLANCK+\verb|i100| & 0.0267 & 3.68 & 1.19 & 2.61 \\ [-2ex]
\enddata
\end{deluxetable}

@@

The MCMC fitting procedure described in $\S$\ref{sec:fitting} is performed
separately for both model 1 (FIRAS+\verb|i100|) and model 2 
(\PLANCK+\verb|i100|), each defined by their respective global parameters 
listed in Table \ref{tab:global}.

@@

The \PLANCK~100-353 GHz data are provided in units of $K_{CMB}$, while 
\verb|i100| and the higher frequency HFI maps are provided in units of 
MJy/sr.

\subsection{Fitting Parameters}
In order to fit the \PLANCK/\verb|i100| dust SED, we must combine the 
underlying two-component spectrum $M_{\nu}$ with the bandpass corrections 
$b_{\nu_i}$ to yield predictions which can be compared against the observed 
broadband intensities. The model-predicted broadband intensities 
$\tilde{I}_{\nu_i}$ are given by:
